---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# taco

R bindings for the python official repository for the paper "End-to-End Compression for Tabular Foundation Models".

official python repo for more information: https://github.com/machinelearningnuremberg/TACO  

<!-- badges: start -->
<!-- badges: end -->

The goal of taco is to provide R interface to TACO, TabPFN-TACO, an end-to-end tabular compression model, increasing inference speed by roughly 94x. 

## Installation

You can install the development version of taco like so:

``` r
pak::pak("frankiethull/taco")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(taco)
library(rsample)

corn_data <- maize::corn_data

corn_splits <- initial_validation_split(corn_data)
train <- training(corn_splits)
validate <- validation(corn_splits)
test <- testing(corn_splits)
```


### Classification 

```{r}
fit_cls <- taco_fit(
  train |> dplyr::select(-type),
  train$type,
  device = "cpu"
)

proba_preds <- taco_predict(fit_cls, test |> dplyr::select(-type))

proba_preds |> head()
```